---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(geonetwork)
```
# geonetwork

Classes and methods for handling networks or graphs whose nodes are
geographical (i.e. locations in the globe). Create, transform, plot.


## Installation

<!-- You can install the released version of geonetwork from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("geonetwork") -->
<!-- ``` -->

`geonetwork` is in development. You can install the current version
from GitLab with:

```{r eval = FALSE}
remotes::install_gitlab("famuvie/geonetwork")
```


## Example

### Creation

A `geonetwork` is an object of class `igraph` whose nodes have
_geospatial_ attributes (i.e. coordinates and CRS).

Consider the distances (in km) between 21 cities in Europe from the
`datasets` package. A simple way of constructing a `geonetwork` is
by combining a data.frame of `nodes` with one of `edges`:

```{r creation}
cities <- cbind(
  city = labels(datasets::eurodist),
  ggmap::geocode(labels(datasets::eurodist), source = "dsk")
)

distances <- 
  expand.grid(
    origin = labels(datasets::eurodist),
    destin = labels(datasets::eurodist),
    stringsAsFactors = FALSE,
    KEEP.OUT.ATTRS = FALSE
  )
distances <- 
  cbind(
    distances[distances$destin < distances$origin,],
    distance = as.numeric(datasets::eurodist)
  )

str(cities)
str(distances)

eurod_net <- geonetwork(distances, nodes = cities, directed = FALSE)
```

Several assumptions were made here unless otherwise specified:

- The first column in `cities` was matched with the first two columns
in `distances`.

- The second and third columns in `cities` were assumed to be 
longitude and latitude in decimal degrees in a WGS84 CRS.

- The remaining column in `distances` was treated as an edge _weight_.

Now we can readily plot the network, optionally with some additional 
geographical layer for context:

```{r dummy-object, warning = FALSE, include = FALSE}
eurod_net <- 
  sf::st_sf(
    city = cities$city, 
    geom = sf::st_sfc(
      sf::st_multipoint(as.matrix(cities[,-1]), dim = "XY"),
      crs = 4326
    )
  )

```


```{r plotting}
library(sp)
plot(as(eurod_net, "Spatial"))  # sp
maps::map(add = TRUE, fill = TRUE, col = "lightgray")
points(as(eurod_net, "Spatial"))  # sp


# library(ggplot2)
# ggplot() +
#   geom_sf(eurod_net_dummy) +
#   geom_sf(spData::world)
```

